---
output:
  word_document: default
  html_document: default
---


```{r}
library(rtweet)
library(tidytext)
library(igraph)
library(dplyr)
library(ggraph)
library(sentimentr)
library(sqldf)
library(tidyr)
library(ggplot2)
```

```{r}
require(curl)
tweets <- na.omit(read.csv(curl("https://raw.githubusercontent.com/PravGitHub/Sentiment-Analysis-with-R/master/tweets.csv"),stringsAsFactors = FALSE))
nrow(tweets)
head(tweets)
```

```{r}
nrow(unique(tweets))
```

```{r}
ts_plot(tweets,by="days")
```

## Seperating into date and time:

```{r}
tweets = separate(tweets,"created_at",c("date","time"),sep=" ")
head(tweets)
```

## Getting the number tweets for each day

```{r}
sqldf("select date, count(date) from tweets group by date")
```

### Since 2020-03-29 and 2020-04-06 have a lot fewer tweets compared to the others, we will eliminate these two.

```{r}
tweets <- subset(tweets,date!= '2020-03-29')
tweets <- subset(tweets,date!= '2020-04-06')

```

## Verifying the elimination

```{r}
sqldf("select date, count(date) from tweets group by date")
```

## Finding the sentiments

```{r}
sentiment=sentiment_by(tweets$text)
```
```{r}
head(sentiment)
nrow(sentiment)
nrow(tweets)
```

## Finding the quartiles of the sentiments

```{r}
summary(sentiment$ave_sentiment)
```
```{r}
res = data.frame(sentiment$ave_sentiment,tweets$date)
colnames(res)=c("sentiment","date")
head(res)
```

## Getting the day-wise count

```{r}
sec <- sqldf("select date, count(sentiment) as count from res group by date")
sec
```

# Partitioning based on quartiles

## Min to First quartile

```{r}
sec1 <- sqldf("select date, count(sentiment) as first_q from res where sentiment>=-2.20663 and sentiment<=-0.02839 group by date")
sec1
```

## First quartile to Second quartile (median)

```{r}
sec2 <- sqldf("select date, count(sentiment) as second_q from res where sentiment>-0.02839 and sentiment<=0.06389 group by date")
sec2
```

## Second quartile to third quartile

```{r}
sec3 <- sqldf("select date, count(sentiment) as third_q from res where sentiment>0.06389 and sentiment<=0.16599 group by date")
sec3
```

## Third quartile to Max

```{r}
sec4 <- sqldf("select date, count(sentiment) as fourth_q from res where sentiment>0.16599 and sentiment<=2.09752 group by date")
sec4
```

## Consolidating all the data

```{r}
sec = cbind(sec,sec1$first_q,sec2$second_q,sec3$third_q,sec4$fourth_q)
colnames(sec)[3]<-"first_q"
colnames(sec)[4]<-"second_q"
colnames(sec)[5]<-"third_q"
colnames(sec)[6]<-"fourth_q"

sec
```

## Converting the count values to percentage values

```{r}
sec$first_q = sec$first_q/sec$count * 100
sec$second_q = sec$second_q/sec$count * 100
sec$third_q = sec$third_q/sec$count * 100
sec$fourth_q = sec$fourth_q/sec$count * 100
sec
```

# Plotting the results

```{r}
ggplot(data=sec,aes(x=date,y=first_q,color="red",group=1))+geom_line()+geom_line(data = sec,aes(x=date,y=second_q,color="violet"))+geom_line(data = sec,aes(x=date,y=third_q,color="blue"))+geom_line(data = sec,aes(x=date,y=fourth_q,color="green"))

```

```{r}
require(corrplot)
correlation <- cor(sec[3:6])
correlation
corrplot(correlation,method = "circle")
```


# Conclusions

### The percentage of highly negative tweets (shown by red) sees a sharp increase.

### The percentage of moderately negative tweets (shown by violet) sees a steady decrease.

### The percentage of moderately positive tweets (shown by blue) peaks early on and then drops.

### The percentage of highly positive tweets (shown by green) is low at the beginning and then increased.

